\makeglossaries

\newacronym{hpc}{HPC}{'High Performance Computing'}
\newacronym{ui}{UI}{'User Interface'}
\newacronym{mpi}{MPI}{'Message Passing Interface'}
\newacronym{lxc}{LXC}{'LinuX Containers'}
\newacronym{nfs}{NFS}{'Network File System'}
\newacronym{slurm}{SLURM}{'Simple Linux Utility for Resource Management'}
\newacronym{hpcg}{HPCG}{'High Performance Conjugate Gradient'}
\newacronym{rhel}{RHEL}{'RedHat Enterprise Linux'}
\newacronym{cae}{CAE}{'Computer Aided Engineering'}
\newacronym{cfd}{CFD}{'Computational Fluid Dynamics'}
\newacronym{hpcac}{HPCAC}{'HPC Advisory Council'}
\newacronym{sysop}{SysOp}{'System Operations'}
\newacronym{openfoam}{OpenFOAM}{'Open Source Field Operation and Manipulation'}


%% Glossary
\newglossaryentry{cgrp}{name=CGroups, description={Kernel based framework to limit the resource usage.}}
\newglossaryentry{ec}{name=EC, description={error code}}
\newglossaryentry{fqdn}{name=FQDN, description={Fully Qualified Domain Name}}
\newglossaryentry{nagios}{name=NAGIOS, description={Health check and alerting system widely used within the IT.}}
\newglossaryentry{openmp}{name=OpenMP, description={Open Multi-Processing, is an API that provides a shard memory among multiple servers.}}
\newglossaryentry{omp}{name=Open MPI, description={oMPI}}
\newglossaryentry{cos6}{name=CentOS 6.5, description={Community Enterprise Operating System in version 6.5, derived from the sources of Red Hat Enterprise Linux 6 (RHEL6).}}
\newglossaryentry{cos7}{name=CentOS 7.0, description={Community Enterprise Operating System in version 7.0, derived from the sources of Red Hat Enterprise Linux 7 (RHEL7).}}
\newglossaryentry{u12}{name=Ubuntu 12.04, description={Ubuntu 12.04.}}
\newglossaryentry{qdr}{name=QDR, description={Quad data rate (or quad pumping) is a communication signaling
        technique wherein data are transmitted at four points in the clock cycle:
        on the rising and falling edges, and at two intermediate points between them.}}

\newglossaryentry{rpm}{name=RPM, description={RPM Package Manager, a package management system created by RedHat. }}

\newglossaryentry{sriov}{name=SR-IOV, description={oMPI}}